FinalManuscript_DISCS_UG

### 2019-05-02 parts/05_conclusions.tex
Final comments from adviser

Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system. Protocols for secure multiplication and exponentiation have been proposed and also applied to more complex image operations such as facial recognition. Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.

Preliminary results have shown that both Paillier and DGK apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR. For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$) which was rather unexpected. However both Paillier and DGK fail to produce accurate results in applying the power-law transformation, with the latter failing to produce discernible results. Based on these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.

@@

>>>>

Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system. Protocols for secure floating-point operations have been proposed and also applied to more complex image operations such as facial recognition.  Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.

We have derived a new closed-form approximation to the logarithm which is more accurate than previous closed-form approximations, while requiring similar computational effort. We have applied this closed-form approximation to achieve non-linear image transformations under homomorphic cryptosystems. Preliminary results have shown that both Paillier and DGK apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR. For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$) which was rather unexpected. However both Paillier and DGK fail to produce accurate results in applying the power-law transformation, with the latter failing to produce discernible results. Based on these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results for image negation and logarithm transformation.

@@

In summary, we make the following conclusions regarding our research questions.
\begin{itemize}
    \item While fully homomorphic cryptosystems such as DGHV and BGV allow for arbitrary secure computation, it is possible to extend a partially homomorphic cryptosystem, such as Paillier and DGK, to allow efficient secure floating-point operations. Secure calculation of non-linear functions, such as the natural logarithm, can be implemented with closed-form approximations.
    \item Out of the cryptosystems tested, the Paillier cryptosystem is the most viable homomorphic cryptosystem for use in secure image processing, as it is the most time-efficient, most accurate and best preserves image quality. However, it is not perfect, as there is an observed inaccuracy with respect to the intented output of the logarithm transformation.
\end{itemize}

### 2019-05-02 thesis.tex
Final comments from adviser

\addappheadtotoc
\begin{appendices}
% \input{parts/08_appendices_a_cryptosystems}
\input{parts/08_appendices_b_numericalapproximations_updated}
\chapter{ACCEPTED PAPERS}
The following pages include related papers accepted in the following conferences.
\begin{itemize}
    \item 19th Philippine Computing Science Congress (PCSC 2019)
    \item 2019 4th International Conference on Multimedia Systems and Signal Processing (ICMSSP 2019)
\end{itemize}
\end{appendices}

>>>>

\addappheadtotoc
\begin{appendices}
% \input{parts/08_appendices_a_cryptosystems}
\input{parts/08_appendices_b_numericalapproximations_updated}
\chapter{ACCEPTED PAPERS}
The following pages include papers accepted in national and international conferences as a part of this thesis.
\begin{itemize}
    \item ``Privacy-Preserving Approximation of Transcendental Functions'', accepted in the \textit{19th Philippine Computing Science Congress} (PCSC 2019).
    \item ``Implementation and Analysis of Homomorphic Facial
    Image Encryption and Manipulation'', accepted in the \textit{2019 4th International Conference on Multimedia Systems and Signal Processing} (ICMSSP 2019).
\end{itemize}
\end{appendices}
